---
title: "Lab 06 - Text Mining"
output: html_document
---

# Learning goals

- Use `unnest_tokens()` and `unnest_ngrams()` to extract tokens and ngrams from text.
- Use dplyr and ggplot2 to analyze text data

# Lab description

For this lab we will be working with a new dataset. The dataset contains transcription samples from https://www.mtsamples.com/. And is loaded and "fairly" cleaned at https://raw.githubusercontent.com/USCbiostats/data-science-data/master/00_mtsamples/mtsamples.csv.

This markdown document should be rendered using `github_document` document.

# Setup the Git project and the GitHub repository

1. Go to your documents (or wherever you are planning to store the data) in your computer, and create a folder for this project, for example, "PM566-labs"

2. In that folder, save [this template](https://raw.githubusercontent.com/USCbiostats/PM566/master/content/assignment/06-lab.Rmd) as "README.Rmd". This will be the markdown file where all the magic will happen.

3. Go to your GitHub account and create a new repository, hopefully of the same name that this folder has, i.e., "PM566-labs".

4. Initialize the Git project, add the "README.Rmd" file, and make your first commit.

5. Add the repo you just created on GitHub.com to the list of remotes, and push your commit to origin while setting the upstream.

### Setup packages

You should load in `dplyr`, (or `data.table` if you want to work that way), `ggplot2` and `tidytext`.
If you don't already have `tidytext` then you can install with

```{r, eval=FALSE}
install.packages("tidytext")
```

### read in Medical Transcriptions

Loading in reference transcription samples from https://www.mtsamples.com/

```{r, warning=FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(tidytext)
library(dplyr)

mt_samples <- read_csv("/Users/sherryshen/Desktop/mtsamples.txt")
mt_samples <- mt_samples %>%
  select(description, medical_specialty, transcription)

head(mt_samples)

#mt_samples$transcription[1]
```

---

## Question 1: What specialties do we have?

We can use `count()` from `dplyr` to figure out how many different categories do we have? Are these categories related? overlapping? evenly distributed?

```{r}
mt_samples %>%
  count(medical_specialty, sort = TRUE)
```

We can see that among medical_specialty, "Surgery" is the most frequent one with n=1103.  

---

## Question 2

- Tokenize the the words in the `transcription` column
- Count the number of times each token appears
- Visualize the top 20 most frequent words

Explain what we see from this result. Does it makes sense? What insights (if any) do we get?

```{r token-transcrip}
library(forcats)

mt_samples %>%
  unnest_tokens(token, transcription) %>%
  count(token, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(token, n)))+
  geom_col()

```
We can see that, among the top 20 words in "transcription", there aren't many words that will raise our interests. 

---

## Question 3

- Redo visualization but remove stopwords before
- Bonus points if you remove numbers as well

What do we see know that we have removed stop words? Does it give us a better idea of what the text is about?

```{r remove-sw-num}
library(stringr)
stop_words
nums=as.character(seq(0,100))

mt_samples %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words)%>%
  filter(!(word %in% nums)) %>%
  count(word, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(word, n)))+
  geom_col()

#trimws() remove spaces before and after a word 
#str_squish() remove extra spaces between 2 words that suppose to have only #one space between. 
```
After removing "stop_words" and "numbers", we can see that, words start to seems interesting now. 

---

# Question 4

repeat question 2, but this time tokenize into bi-grams. how does the result change if you look at tri-grams?

```{r grams}
mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 2) %>%
  count(ngram, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(ngram, n)))+
  geom_col()

mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 3) %>%
  count(ngram, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(ngram, n)))+
  geom_col()

#combine n=2 and n=3
mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 3, n_min = 2) %>%
  count(ngram, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x = n, y = fct_reorder(ngram, n)))+
  geom_col()

```

We can see that when n=3, we have a more interesting combination of words in "transcription". For example: "the operating room".  

---

# Question 5

Using the results you got from questions 4. Pick a word and count the words that appears after and before it.

```{r blood}
library(tidyr)

mt_bigrams <- mt_samples %>%
  unnest_ngrams(ngram, transcription, n = 2) %>%
  separate(ngram, into = c("word1", "word2"), sep = " ") %>%
  select(word1, word2) 

mt_bigrams %>%
  filter(word1 == "blood") %>%
  count(word2, sort = TRUE)

mt_bigrams %>%
  filter(word2 == "blood") %>%
  count(word1, sort = TRUE)

#remove stopwords
mt_bigrams %>%
  anti_join(
    stop_words %>% 
      select(word), by =c("word1" = "word")
    ) %>%
  anti_join(
    stop_words %>% 
      select(word), by =c("word2" = "word")
    ) %>%
  count(word1, word2, sort=TRUE)
  
```
We can see that bi-grams of "blood" appears far more interesting than the one without removing the stop words. 
---

# Question 6 

Which words are most used in each of the specialties. you can use `group_by()` and `top_n()` from `dplyr` to have the calculations be done within each specialty. Remember to remove stopwords. How about the most 5 used words?

```{r groupby}
mt_samples %>%
  unnest_tokens(token, transcription) %>%
  anti_join(tidytext::stop_words, by = c("token" = "word")) %>%
  group_by(medical_specialty) %>%
  count(token) %>%
  top_n(1, n)
  
mt_samples %>%
  unnest_tokens(token, transcription) %>%
  anti_join(tidytext::stop_words, by = c("token" = "word")) %>%
  group_by(medical_specialty) %>%
  count(token) %>%
  top_n(5, n)

```
We can see that "history" is often mentioned in medicial specialty of Allergy and Immunology. 

# Question 7 - extra

Find your own insight in the data:

Ideas:

- Interesting ngrams
- See if certain words are used more in some specialties then others

```{r TF-IDF}
mt_samples %>%
  unnest_tokens(word, transcription) %>%
  count(word, medical_specialty) %>%
  bind_tf_idf(word, medical_specialty, n) %>%
  arrange(desc(tf_idf))
```

We can see that word "carbon hydrate" having the largest TF-IDF meaning that only in the specialty of "Diet and Nutrition", the word " carbon hydrate" is commonly used. 